\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-18 main.Rmd
added interactivity subsection

@@

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between weekdays and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 6pm on weekdays.

@@

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households. Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their weekday energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

>>>>

As a data re-structuring tool, the interactivity of calendar-based display can be easily enabled, as long as the interactive graphic system remains true to the spirit of the grammar of graphics, for example **plotly** in R. As a standalone display, interactive tooltip can be added to show the actual values of a data point when mousing over it in the calendar layout, for example the hourly count with the time of day. It is difficult to sense the values in static display, but the tooltip makes it possible. Options in function `frame_calendar` can be ported to a form of selection buttons or text input. The display will update on the fly accordingly via clicking or inputing, as desired.

Linking calendar displays to other types of charts is of great value to visually explore the interactions with many factors. It most naturally serves as a toolbox of date selection. By selecting and brushing the glyphs in the calendar, it subsequently highlights the elements of corresponding dates in other time-based plots, or vice versa. For example, it would be interesting to learn if very hot/cold days and heavy rain affect the number of people walking in downtown Melbourne, especially outdoor areas. Melbourne's daily temperatures and precipitations can be acquired, and plotted against the dates. The linking between weather data and calendar display is achieved using the common dates.

@@

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between weekdays and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on weekdays. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between weekdays and weekends. As for household 4, their home routine starts after 6pm on weekdays. Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households.

@@

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their weekday energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

### 2018-10-18 main.tex
added interactivity subsection

>>>>

As a data re-structuring tool, the interactivity of calendar-based
display can be easily enabled, as long as the interactive graphic system
remains true to the spirit of the grammar of graphics, for example
\textbf{plotly} in R. As a standalone display, interactive tooltip can
be added to show the actual values of a data point when mousing over it
in the calendar layout, for example the hourly count with the time of
day. It is difficult to sense the values in static display, but the
tooltip makes it possible. Options in function \texttt{frame\_calendar}
can be ported to a form of selection buttons or text input. The display
will update on the fly accordingly via clicking or inputing, as desired.

Linking calendar displays to other types of charts is of great value to
visually explore the interactions with many factors. It most naturally
serves as a toolbox of date selection. By selecting and brushing the
glyphs in the calendar, it subsequently highlights the elements of
corresponding dates in other time-based plots, or vice versa. For
example, it would be interesting to learn if very hot/cold days and
heavy rain affect the number of people walking in downtown Melbourne,
especially outdoor areas. Melbourne's daily temperatures and
precipitations can be acquired, and plotted against the dates. The
linking between weather data and calendar display is achieved using the
common dates.
